\vskip-0.6in \Large Political Uncertainty

### 2015-09-25 GS-extension.tex
took out wrong statements that resulted from dividing by zero

\newpage
\subsection{Math for Discrete Model}
The math that follows from Equation \ref{eq:logistic}:
\begin{itemize}
	\item Let
		\begin{enumerate}
			\item $X = -\alpha + b(0)$ 
			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$
		\end{enumerate}
	\item Then Equation \ref{eq:logistic} is equivalent to:
		\begin{equation}
			\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z} }
					\label{eq:logistic2}
		\end{equation}
		\[
			\frac{2 + e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\[
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\begin{equation}
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Likewise, we have
		\begin{equation}
			\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Setting the left-hand size of these two equations equal to each other,
		\[
		  \frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}
		\]
		\[
		  \frac{e^{-X-Z} + e^{-Y-Z}}{1+e^{-Z}}= \frac{e^{-X-Y} + e^{-Y-Z}}{1+e^{-Y}}
		\]
		\[
		  e^{-X-Z} + e^{-Y-Z} + e^{-X-Y-Z} +e^{-2Y-Z}= e^{-X-Y} + e^{-Y-Z} + e^{-X-Y-Z} +e^{-Y-2Z}
		\]
		\[
		  e^{-X-Z} +e^{-2Y-Z}= e^{-X-Y} +e^{-Y-2Z}
		\]
		\[
		  e^{-X}\left(e^{-Z} - e^{-Y} \right) = e^{-Y-Z}\left(e^{-Z} - e^{-Y} \right)
		\]
		\[
		  e^{-X} = e^{-Y-Z}
		\]
		\begin{equation}
		  -X = -Y-Z
			\label{eq:X}
		\end{equation}
		By symmetry, we also have
		\begin{equation}
		  -Y = -X - Z
			\label{eq:Y}
		\end{equation}
		\begin{equation}
		  -Z = -X - Y
			\label{eq:Z}
		\end{equation}
		Substituting Equation \ref{eq:Z} into Equation \ref{eq:X}
		\[
		  - X = - Y - X - Y \Rightarrow 0 = 2Y \Rightarrow Y = 0
		\]
		Substituting from $Y = 0$ into Equation \ref{eq:X}, we have $X = Z$. Substituting both into Equation \ref{eq:Y}, we have $0 = Z + Z$, which implies $Z = 0$. Likewise for $X$. Thus we must have
		\[
		  X = Y = Z = 0
		\]		
\end{itemize}

>>>>

\vskip.5in
Simulations show that for many sets of parameters, $b\left(0\right)$ and $b\left(\frac{1}{2}\right)$ are positive while $b\left(-\frac{1}{2}\right) = 0$.
\begin{itemize}
	\item Then $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right) = -\frac{\beta}{2} - \alpha $
	\item $\lambda_Z$ is likely positive
	\item $\lambda_X = \lambda_Y = 0$
\end{itemize}

\newpage
\subsection{Math for Discrete Model}
The math that follows from Equation \ref{eq:logistic}:
\begin{itemize}
	\item Let
		\begin{enumerate}
			\item $X = -\alpha + b(0)$ 
			\item $Y = \frac{\beta}{2} - \alpha + b\left(\frac{1}{2}\right)$
			\item $Z = -\frac{\beta}{2} - \alpha + b\left(-\frac{1}{2}\right)$
		\end{enumerate}
	\item Then Equation \ref{eq:logistic} is equivalent to:
		\begin{equation}
			\frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z} }
					\label{eq:logistic2}
		\end{equation}
		\[
			\frac{2 + e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} - 2\frac{1}{1+e^{-X}}  \frac{1}{1+e^{-Y}} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\[
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} = \frac{\left(1+e^{-Z}\right)^2}{W_B \: e^{-Z}}
		\]
		\begin{equation}
			\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Likewise, we have
		\begin{equation}
			\frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}= \frac{1}{W_B}
		\end{equation}
		Setting the left-hand size of these two equations equal to each other,
		\[
		  \frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left(1+e^{-Z}\right)^2}= \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left(1+e^{-Y}\right)^2}
		\]
		\[
		  \frac{e^{-X-Z} + e^{-Y-Z}}{1+e^{-Z}}= \frac{e^{-X-Y} + e^{-Y-Z}}{1+e^{-Y}}
		\]
		\[
		  e^{-X-Z} + e^{-Y-Z} + e^{-X-Y-Z} +e^{-2Y-Z}= e^{-X-Y} + e^{-Y-Z} + e^{-X-Y-Z} +e^{-Y-2Z}
		\]
		\[
		  e^{-X-Z} +e^{-2Y-Z}= e^{-X-Y} +e^{-Y-2Z}
		\]
		\[
		  e^{-X}\left(e^{-Z} - e^{-Y} \right) = e^{-Y-Z}\left(e^{-Z} - e^{-Y} \right)
		\]
